---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
    self_contained: true
---


## Loading and preprocessing the data
```{r echo=TRUE,cache=FALSE}
act <- read.csv('activity.csv', header=T)
#act$date <- as.Date(act$date, "%Y-%m-%d")
```


## What is mean total number of steps taken per day?
```{r echo=TRUE,warning=FALSE,message=FALSE}
library(ggplot2)
library(xtable)
dailysteps <- aggregate(steps ~ date, data=act, sum, na.rm=TRUE)
qplot(steps, data=dailysteps, geom="histogram")+labs(title='daily sum steps historgram')
```
### daily mean steps
```{r results='asis'}
dailysteps <- aggregate(steps ~ date, data=act, mean, na.rm=TRUE)
print(xtable(dailysteps), type='html', include.rownames=FALSE)
```
### daily median steps
```{r results='asis'}
dailysteps <- aggregate(steps ~ date, data=act, median, na.rm=TRUE)
print(xtable(t(dailysteps)), type='html', include.rownames=FALSE)
```
## What is the average daily activity pattern?
```{r}
dailypattern <- tapply(act$steps, act$interval, mean, na.rm=TRUE)
qplot(as.numeric(names(dailypattern)), dailypattern, geom='line', xlab="minutes") 
```
### max activity at minutes
```{r}
names(which.max(dailypattern))
```

## Imputing missing values
```{r}
library(dplyr)
nona <- sum(is.na(act$steps))
act2 <- act %>%
 group_by(interval) %>%
 mutate(steps=ifelse(is.na(steps), median(steps, na.rm=TRUE),steps)) 
nona2 <- sum(is.na(act2$steps))

```
there are total `r nona` rows data contains 'NA'  
and after fillin there are `r nona2`
```{r warning=FALSE,message=FALSE}
dailysteps <- aggregate(steps ~ date, data=act2, sum)
qplot(steps, data=dailysteps, geom="histogram")+labs(title='daily sum steps historgram after na fillin')
```
### daily mean steps
```{r results='asis'}
dailysteps <- aggregate(steps ~ date, data=act2, mean, na.rm=TRUE)
print(xtable(dailysteps), type='html', include.rownames=FALSE)
```
### daily median steps
```{r results='asis'}
dailysteps <- aggregate(steps ~ date, data=act2, median, na.rm=TRUE)
print(xtable(t(dailysteps)), type='html', include.rownames=FALSE)
```
## Are there differences in activity patterns between weekdays and weekends?
```{r}
act2$weekdays <- factor(ifelse(weekdays(as.Date(act2$date)) %in% c('Saturday', 'Sunday'), 'weekend', 'weekday'))

#dailypattern <- tapply(act2$steps, list(act2$weekdays,act2$interval), mean, na.rm=TRUE)
dailypattern <- act2 %>%
 group_by(weekdays, interval) %>%
 summarise(steps=mean(steps))

p <- ggplot(dailypattern, aes(x=interval, y=steps))
p <- p + geom_line()
p <- p + facet_wrap(~weekdays)
print(p)
```
